Changes From Preregistration

### 2020-06-15 preregistration_changes.rmd
- updated feedback - updated website
- implemented feedback from ST

The preregistration can be found here. In what follows, we present where we decided to deviate from preregistration.

@@

 -	We changed the order of the hypotheses.
 -	We changed the wording of the hypotheses (but not the content)
    -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
    - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”

@@

In the preregistration, we stated that we would measure expected benefits by means of 5 general items (“Using the participation platform had many benefits for me”). However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration stated that additional variables that one does not plan to analyze do not need to be preregistered). These specific measures of gratifications were hence used for exploratory analyses.

@@

Originally, we operationalized trust for three entities (i.e., provider, website, and other users) with four subdimensions (i.e., general trust, ability, benevolence, and integrity). Only later did we realized that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured. As a result, in the paper we differentiated both dimensions.

@@

Given that we found not apparent effects of the three websites on the privacy calculus, we did not test for indirect effects as proposed in the preregistration. We additionally also controlled for education (we probably forgot to explicitly mention it in the preregistration; results do not differ, but we think it should be included).

@@

In the preregistration, we stated that we would analyze the additional exploratory analyses using Bonferroni-Holm correction. However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one would need to account for is potentially infinite. Instead, we decided not to make strong inferences on the basis of the exploratory analyses, and report p-values / confidence intervals only descriptively as a measure of precision.

>>>>

The preregistration can be found [here](https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). In what follows, we present where we decided to deviate from the preregistration.

@@

 -	We've changed the order of the hypotheses.
 -	We've changed the wording of the hypotheses (but not the content)
    -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
    - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”
 -  We've changed the enumeration of the hypotheses (but not the overall number). 
    - Before, hypotheses were enumerated from 1-13.
    - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.

@@

In the preregistration, we stated that we would measure expected benefits by means of 5 general items (“Using the participation platform had many benefits for me”). However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration manual stated that additional variables that one does not plan to analyze do not need to be preregistered). These specific measures of gratifications were hence used for exploratory analyses.

@@

Originally, we operationalized trust for three entities (i.e., provider, website, and other users) using four subdimensions (i.e., general trust, ability, benevolence, and integrity). Only later did we realize that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured. As a result, in the paper we now differentiate both dimensions.

@@

Given that we found not apparent effects of the three websites on the privacy calculus, we did not test for indirect effects as proposed in the preregistration. We additionally also controlled for education (we forgot to explicitly mention this control variable in the preregistration; results do not differ, but we think it should be included, which is why we did).

@@

In the preregistration, we stated that we would analyze the additional exploratory analyses using Bonferroni-Holm correction. However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one could potentially account for is infinite. Instead, we decided not to make strong inferences on the basis of the exploratory analyses, and report p-values / confidence intervals only descriptively as a measure of precision.
